BtheB Group 1 Write-up
========================================================

**TODO** : Our names will go here (?)

## Introduction

This is a dataset containing information from a clinical trial with "Beat the Blues", an interactive 
multimedia program of cognitive-behavioural techniques. Since there are way more patients suffering from anxiety 
and depression than therapists, the study of the dataset makes the case that this program can indeed help with 
the treatment. One of the metrics used to gauge depression levels was BDI or Beck Depression Inventory. 

The dataset contains one hundred observations of one hundred patients and eight variables. 
BDI was tracked before treatment, after two  months and then after one, three and six month follow-ups. 
Two groups are studied, one that uses the BtB program and one that has the usual anti-depression treatment. 
Those can be further splitted to sub-groups of patients that were taking anti-depressant drugs. 


**TODO** : Do you think anything else should be added? Perhaps what's the main point in our report,
i.e the variables we compare. 


**TODO** : Citation is needed (perhaps with knitcitations?)
This data frame comes from the following study. 

*J. Proudfoot, D. Goldberg, A. Mann, B. S. Everitt, I. Marks and J. A. Gray, (2003). Computerized, interactive, multimedia cognitive-behavioural program for anxiety and depression in general practice. Psychological Medicine, 33(2), 217–227.*



## On missing values

```{r}
library(ggplot2)
library(MASS)
library(HSAUR2)

BtheB <- BtheB
attach(BtheB)
summary(BtheB)

plot(bdi.3m~bdi.2m)
m2m3m <- lm(bdi.3m~bdi.2m,data=BtheB)
abline(m2m3m)
summary(m2m3m)

qplot(bdi.2m, bdi.3m, data = BtheB, facets = . ~ treatment,geom=c("point","smooth"), method="lm")
```

```{r}
m2<-rbind(,sum(is.na(BtheB$bdi.2m) & BtheB$treatment=="BtheB"), sum(is.na(BtheB$bdi.2m) & BtheB$treatment=="TAU") +sum(is.na(BtheB$bdi.2m) & BtheB$treatment=="BtheB"))
m3<-rbind(sum(is.na(BtheB$bdi.3m) & BtheB$treatment=="TAU"),sum(is.na(BtheB$bdi.3m) & BtheB$treatment=="BtheB"), sum(is.na(BtheB$bdi.3m) & BtheB$treatment=="TAU") +sum(is.na(BtheB$bdi.3m) & BtheB$treatment=="BtheB"))
m4<-rbind(sum(is.na(BtheB$bdi.3m) & is.na(BtheB$bdi.2m) & BtheB$treatment=="TAU"),sum(is.na(BtheB$bdi.3m) & is.na(BtheB$bdi.2m) & BtheB$treatment=="BtheB"),sum(is.na(BtheB$bdi.3m) & is.na(BtheB$bdi.2m) & BtheB$treatment=="BtheB")+sum(is.na(BtheB$bdi.3m) & is.na(BtheB$bdi.2m) & BtheB$treatment=="TAU") )
missing<-cbind(m2,m3,m4)
col<-c("bdi.2m", "bdi.3m", "Both")
row<-c("TAU", "BtheB", "Total")
row.names(missing)<-row
colnames(missing)<-col
missing

100-27

sum(BtheB$treatment=="TAU")-missing[1,2]
sum(BtheB$treatment=="BtheB")-missing[2,2]

```
The 3 that are missing from the m2 data are also missing from the m3 data, so we have 73 useuable observations.  Of these 73 we have a close number for each treament; 36 had the treatment TAU and 37 had the treatment, "BtheB".  It's nice that we have a almost even number of participants in each group.  Though the sample size seems too small, it is far better than if we had used either of the last 2 variables.


